% LaTeX resume using res.cls
\documentclass[line,margin]{res}
\usepackage{ifthen}
\usepackage{tabularx,booktabs}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textheight}{10in}
%\setlength{\textwidth}{7in}
\setlength{\voffset}{-0.5in}
%\setlength{\hoffset}{-0.5in}
\oddsidemargin=-0.5in
\resumewidth=7.5in

\newsectionwidth{20pt}

\newcommand{\ifthen}[2]{\ifthenelse{#1}{#2}{}}

%\newcommand{\compactlist}{
%  \itemize
%  \setlength{\itemsep}{0pt}%
%  \setlength{\parskip}{0pt}%
%%  \setlength{\parsep}{0pt}
%}

\newenvironment{compactlist}{
	\begin{itemize}\itemsep=0pt
}{
	\end{itemize}
}

%%% We can put stuff inside a \CVOnly{} tag to make it only show up for a CV :)
\providecommand{\ResumeCV}{0}% fallback definition % 0=Resume, 1=CV
%\def\ResumeCV{0}  % 0=Resume, 1=CV
\ifthen { \ResumeCV = 0 }
        { \newcommand{\ResumeOnly}[1]{#1}
          \newcommand{\CVOnly}[1]{}
          \newcommand{\CVOnlySmall}[1]{{\small \CVOnly{#1}}}
          \newcommand{\ResumeOnlySmall}[1]{{\small \CVOnly{#1}}}
          \newcommand{\BothSmall}[1]{{\small #1}}   }
\ifthen { \ResumeCV = 1 }
        { \newcommand{\ResumeOnly}[1]{}
          \newcommand{\CVOnly}[1]{#1}
          \newcommand{\CVOnlySmall}[1]{{\CVOnly{#1}}}
          \newcommand{\ResumeOnlySmall}[1]{{\CVOnly{#1}}}
          \newcommand{\BothSmall}[1]{{#1}}    }

\newcommand{\hide}[1]{}

\newcommand{\boldName}[1]{\textbf{#1}}

\begin{document}
%\resumewidth{100pt}

\name{Adam Eric Leeper}
% \address used twice to have two lines of address
\address{469 Homer Ave, Palo Alto, CA 94301}
\address{650.762.6844}
\address{adamleeper@gmail.com}
\address{www.adamleeper.com}
%\address{www.stanford.edu/$\sim$aleeper }

%\setpapersize{USletter}
%\setmarginsrb{1in}{1in}{1in}{1in}{0pt}{0mm}{0pt}{0mm}

\begin{resume}
%
\section{\underline{EXPERIENCE}}
\vspace{1.0pc}
{\bf Senior Systems Engineer} - hiDOF, Inc., South San Francisco, CA  \hfill \textbf{July `13 - present}
\begin{compactlist}
\item Key software developer for major client. C++ system design, algorithm development, and build-system support.
\item Projects in wheeled vehicle motion planning, visual inertial navigation, and visual monocular SLAM.
\end{compactlist}
%
{\bf Research Intern} - Willow Garage, Inc., Menlo Park, CA \hfill \textbf{Sept. `10 - June `13}
\begin{compactlist}
%\item Created systems, controllers, and user interfaces for teleoperated mobile manipulation.
\item Developed and maintained the first PR2 teleoperation application using interactive markers, 
which saw extensive use by other researchers and formed a major component of the \textit{Robots for Humanity} project.
\item Developed novel optimization-based controller and user interfaces for assisted collision-free teleoperation.
\item Conducted user experiments and authored papers published in major robotics conferences.
%\item Authored new ROS packages for 6-DOF/haptic user interaction and robot teleoperation.
\end{compactlist}
%
{\bf Graduate Researcher} - Salisbury Robotics Lab, Stanford, CA \hfill \textbf{Aug. `08 - June `13}
\begin{compactlist}
\item Developed new algorithms for haptic rendering and robot control (in collaboration with Willow Garage).
\item Implemented miniature stereo camera sensor for a robot gripper (PCB design, mechanical hardware prototyping).
\end{compactlist}
%
\CVOnly{
{\bf Electrical Engineering Intern} - Qual-Tron, Inc., Tulsa, OK \hfill \textbf{March `06 - Feb. `07}
\begin{compactlist}
\item Designed and implemented test procedures for IR and magnetic sensor products.
\item Led redesign of a magnetic sensor product to reduce cost and simplify assembly.
\end{compactlist}
}
%
\hide{
\\[0.4pc]{\bf Summer Intern} - Atmel Corporation \hfill \textbf{Summer `05}
\\[0.4pc]{\bf Summer Research Intern} - NASA Glenn Research Center \hfill \textbf{Summer `04}%
}
%
{\bf \underline{Consulting:}}
\\[0.2pc]{\bf Motion Genesis, LLC} - Developed web-based visualization software for multi-body systems. \hfill \textbf{Spring `11 - Fall `13}%
{\\[0.0pc]{\bf Applied Materials, Inc.} - Subcontracting consultant for robot motion visualization. \hfill \textbf{Fall `12}}%
\CVOnly{\\[0.0pc]{\bf Charm Labs} - Dynamics and control. Confidential. \hfill \textbf{Summer `12}}%
%
%
\section{\underline{SKILLS}}
\vspace{1.0pc}
%\textbf{Overview:} Strong expertise in robotics, dynamics, controls, and applied mathematics.
\textbf{Applied Math - } Expert in dynamics, kinematics, and 3D geometry as applied to robotics, simulation, and graphics.
\\[0.0pc]\textbf{Software Languages - } Extensive use of C++ and Python (6 years, 3 in production) in large software projects with a focus on quality and maintainability. Proficient in web programming (Javascript, HTML, CSS) and MATLAB.
\\[0.0pc]\textbf{Software Tools - } Expert knowledge of ROS. Experience with MoveIt!, PCL, OpenCV, OpenGL, and Qt.
Development experience in Ubuntu Linux (expert) and Windows (proficient) using version control (git, svn) and issue tracking. %Familiar with Windows development. 
\\[0.0pc]\textbf{Electronics - } Circuit design/debugging, prototype PCB layout/fabrication, embedded systems.
\\[0.0pc]\textbf{Hardware - } General machine shop rapid-prototyping skills, and proficient in CAD tools (Solidworks).
\\[0.0pc]\textbf{Languages - } English (native), Spanish (fluent), French (proficient reading and writing).
\\[0.0	pc]\textbf{Other - } Private pilot, recording engineer, bassist.
%
%
\section{\underline{EDUCATION}}
\vspace{1.0pc}
\textbf{Ph.D.} Mechanical Engineering under Professor Ken Salisbury, Stanford University, 3.94 GPA
\hfill \textbf{June `13}%
{ {\small
%\\[0.0pc]{\bf Advisor:} Professor Kenneth Salisbury
\\[0.0pc]{\bf Thesis:} Robot Telemanipulation in Unstructured Environments: Sensors, Algorithms, Interfaces.
\\[-0.6pc]} }
%
\\[0.0pc]\textbf{M.S.} Mechanical Engineering, Stanford University, 3.97 GPA \hfill  \textbf{March `09}
\\[0.0pc]\textbf{B.S.} Engineering Physics, The University of Tulsa, 3.99 GPA \hfill \textbf{May `07}
%

%
%
\section{\underline{TEACHING}}
\vspace{1.0pc}
%{\bf Instructor: }
%\\[0.0pc]
{\bf Instructor:} ENGR 14 Statics, Stanford University, 77 students. \hfill \textbf{\CVOnly{Spring }2014}%
\\[0.0pc]
{\bf Instructor:} ME 101 Dynamics, San Jose State University\ResumeOnly{, 50 students}\CVOnly{, 35 students}. \hfill \textbf{\ResumeOnly{2011, 2012,} \CVOnly{Fall }2013}%
%
\\[0.0pc]
\CVOnly{
\begin{tabularx}{\textwidth}{@{}l@{ }Xr@{}}
	         {\bf Instructor:} & ME 101 Dynamics, San Jose State University\CVOnly{, 49 students}. & \hfill \textbf{Fall 2012}%
	%\\[0.0pc]                  & Student-rated 4.8/5.0 for overall teaching quality. &
	\\[0.0pc]{\bf Instructor:} & ME 101 Dynamics, San Jose State University, 56 students. & \hfill \textbf{Fall 2011}
	%\\[0.0pc]                  & Student-rated 4.6/5.0 for overall teaching quality. &
\end{tabularx}
}
%
{\bf Instructor:} Programming and Robotics, EPGY Summer Institutes at Stanford. \hfill \textbf{\CVOnly{Summer}
2010}%
%
\CVOnly{
\\[0.4pc]
\begin{tabularx}{\textwidth}{@{}l@{ }l@{ - }Xr@{}}
Course Assistant: & ME 331b & Dynamics and Control with Paul Mitiguy. 
& \textbf{\CVOnly{Spring }2012}
\\[0.0pc]
Course Assistant: & CS 277 & Experimental Haptics with Ken Salisbury. 
& \textbf{\CVOnly{Winter }2011}
\\[0.0pc]
Course Assistant: & CS 223a & Robotics with Oussama Khatib. 
& \textbf{\CVOnly{Winter }2010}
\\[0.0pc]
Course Assistant: & ENGR 15 & Dynamics with Paul Mitiguy. 
& \textbf{\CVOnly{Fall }2009}
\end{tabularx}
}
%
%
\ResumeOnly{\section{\underline{SELECTED PUBLICATIONS}}}
\CVOnly{\section{\underline{PUBLICATIONS}}}
\vspace{1.2pc}
%
%\CVOnly{\vspace{0.2pc}\textbf{Journal Articles}\\[0.4pc]}
%
%
\BothSmall{\boldName{A. Leeper}, K. Hsiao, M. Ciocarlie, I. Sucan, and K. Salisbury.
Methods for Collision-Free Arm Teleoperation in Clutter Using Constraints from 3D Sensor Data.
2013 International Conference on Humanoid Robots. October, 2013. Atlanta, Georgia. \\[0.4pc]}
%
\CVOnlySmall{\boldName{A. Leeper}, K. Hsiao, M. Ciocarlie, I. Sucan, K. Salisbury.
Assisted Arm Teleoperation in Clutter Using Constraints from 3D Sensor Data. In 2nd Workshop on Robots in Clutter:
Preparing robots for the real world (in conjunction with RSS). June 2013, Berlin, Germany. \\[0.4pc]}
%
\CVOnlySmall{Chen, Tiffany., Ciocarlie, Matei., Cousins, Steve., Grice, Phillip M.., Hawkins, Kelsey., Hsiao, Kaijen., Kemp, Charlie., King, ChihHung., Lazewatsky, Daniel., \boldName{Leeper, Adam Eric.}, Nguyen, Hai., Paepcke, Andreas., Pantofaru, Caroline., Smart, William., and
Takayama, Leila.
%Robots for Humanity: A Case Study in Assistive Mobile Manipulation.
Robots for humanity: using assistive robotics to empower people with disabilities.
IEEE Robotics and Automation Magazine
special issue on Assistive Robotics. Volume 20, Issue 1, 2013. \\[0.4pc]}
%
\CVOnlySmall{A. Pratkanis, \boldName{A. Leeper}, K. Salisbury. Replacing the Office Intern: An Autonomous Coffee Run with a Mobile Manipulator. ICRA, May 2013, Karlsruhe, Germany. \\[0.4pc]}
%
\CVOnlySmall{M. Ciocarlie, K. Hsiao, \boldName{A. Leeper}, D. Gossow. Mobile Manipulation Through an Assistive Home Robot. IROS, October 2012, Algarve, Portugal. \\[0.4pc]}
%
\BothSmall{\boldName{A. Leeper}, S. Chan, and K. Salisbury. Point Clouds Can Be Represented as Implicit Surfaces for Constraint-Based Haptic Rendering. ICRA, May 2012, St. Paul, MN. \\[0.4pc]}
%
\CVOnlySmall{\boldName{A. Leeper}, S. Chan, K. Hsiao, M. Ciocarlie, K. Salisbury. Constraint-based Haptic Rendering for Teleoperated Robot Grasping. IEEE Haptics Symposium, March 2012, Vancouver, Canada. \\[0.4pc]}
%
\BothSmall{\boldName{A. Leeper}, K. Hsiao, M. Ciocarlie, L. Takayama, D. Gossow. Strategies for Human-in-the-Loop Robotic Grasping. HRI, March 2012, Boston, MA. \\[0.4pc]}
%
\CVOnlySmall{R. Brewer, \boldName{A. Leeper}, K. Salisbury. A Friction Differential and Cable Transmission Design for a 3-DOF Haptic Device with Spherical Kinematics. IROS, Sept. 2011, San Francisco, CA. \\[0.4pc]}
%
\CVOnlySmall{D. Gossow, \boldName{A. Leeper}, D. Hershberger, M. Ciocarlie. Interactive Markers: 3-D User Interfaces for ROS Applications [ROS Topics]. IEEE Robotics and Automation Magazine, December 2011. \\[0.4pc]}
%
\CVOnlySmall{\boldName{A. Leeper}, S. Chan, and K. Salisbury. Constraint-based 3-DOF Haptic Rendering of Arbitrary Point Cloud Data. RSS Workshop on RGB-D Cameras, June 2011, Los Angeles, CA. \\[0.4pc]}
%
\BothSmall{\boldName{A. Leeper}, K. Hsiao, E. Chu, and K. Salisbury. Using Near-Field Stereo Vision for Robotic Grasping in Cluttered Environments. ISER, Dec. 2010, Delhi, India.  \CVOnlySmall{\\[0.4pc]} }
%
\CVOnlySmall{Caruso, John F; Hari, P; \boldName{Leeper, Adam E}; Coday, Michael A; Monda, Julie K; Ramey, Elizabeth S; Hastings, Lori P; Golden, Mallory R; Davison, Steve W. Impact of Acceleration on Blood Lactate Values Derived From High-Speed Resistance Exercise. Journal of Strength \& Conditioning Research. 23(7):2009-2014, October 2009.  \\[0.4pc]}
%
\CVOnlySmall{Caruso J.F., Hari P., Coday M.A., \boldName{Leeper A.}, Ramey E.S., Monda J.K., Hastings L.P., and Davison S. (2008). Performance evaluation of a high-speed inertial exercise trainer. The Journal of Strength \& Conditioning Research. 22(6): 1760-1768. \\[0.4pc]}
%
\CVOnlySmall{\boldName{A. Leeper}, M. Coday, P. Hari, J. Caruso.
Instrumentation of a High-Speed Inertial Exercise Device Using Load Cell Transducers.
Proceedings of 53rd International Instrumentation Symposium, April 2007, Tulsa, OK.}
%
\CVOnly{
\section{\underline{PRESENTATIONS}}
\vspace{1.0pc}
\textbf{\underline{Invited Talks:}}\\[0.4pc]
``Telemanipulation using PCL."
PCL Tutorial at Robotics: Science and Systems 2011. Los Angeles, CA. July 2011. \\[0.4pc]
%
``Instrumentation of a High-Speed Inertial Exercise Device Using Load Cell Transducers."
ISA EXPO 2007. Houston, TX. October 2007. \\[0.4pc]
%
\textbf{\underline{Conference Presentations:}}\\[0.4pc]
%
``Assisted Arm Teleoperation in Clutter Using Constraints from 3D Sensor Data."
2nd Workshop on Robots in Clutter: Preparing Robots for the Real World (in conjunction with RSS).
Berlin, Germany. June 2013. \\[0.4pc]
%
``Point Clouds Can Be Represented as Implicit Surfaces for Constraint-Based Haptic Rendering."
International Conference on Robotics and Automation. St. Paul, MN. May 2012. \\[0.4pc]
%
``Constraint-based Haptic Rendering for Teleoperated Robot Grasping."
IEEE Haptics Symposium. Vancouver, Canada. March 2012. \\[0.4pc]
%
``Constraint-based 3-DOF Haptic Rendering of Arbitrary Point Cloud Data."
RGB-D: Advanced Reasoning with Depth Cameras (workshop in conjunction with RSS). Los Angeles, CA. June 2011. \\[0.4pc]
%
``Using Near-Field Stereo Vision for Robotic Grasping in Cluttered Environments."
International Sympoisum on Experimental Robotics. New Delhi, India. December 2010. \\[0.4pc]
%
``Instrumentation of a High-Speed Inertial Exercise Device Using Load Cell Transducers."
53rd International Instrumentation Symposium. Tulsa, OK. April 2007.
%
}
%
%
\CVOnly{
\section{\underline{OPEN SOURCE SOFTWARE}~(github.com/aleeper)}
\vspace{1.2pc}
\begin{tabularx}{\textwidth}{@{}l@{ - }Xr@{}}
MGView & Javascript web app for visualizing rigid body simulations. Author and maintainer.%
\\[0.0pc]
ROS & Contributor and maintainer of packages in the visualization and device driver stacks.%
\\[0.0pc]
MoveIt! & Contributor to the user interaction and visualization tools within MoveIt! %
\\[0.0pc]
three.js & Contributed STL parser module to enable importing of CAD parts (e.g. from SolidWorks).%
\end{tabularx}
}
%
%
%
\CVOnly{
\section{\underline{AWARDS}}
\vspace{1.0pc}
          2007-2012 National Science Foundation Graduate Research Fellowship
\CVOnly{\\[0.0pc]2007 Stanford Graduate Fellowship }
\CVOnly{\\[0.0pc]2007 John McCamey Award presented by ISA}
\ResumeOnly{\\[0.0pc] Member of Tau Beta Pi and Phi Kappa Phi Honor Societies}
\CVOnly{
\\[0.0pc] Member, Tau Beta Pi Engineering Honor Society
\\[0.0pc] Member, Sigma Pi Sigma Physics Honor Society
\\[0.0pc] Member, Phi Kappa Phi Honor Society
\\[0.0pc] Member, Mortar Board National College Senior Honor Society
}
}
%
\CVOnly{
%\clearpage
\section{\underline{REFERENCES}}
\vspace{1.0pc}
Dr. Kenneth Salisbury, Professor (Research) of Computer Science, 650.465.5700, jks@robotics.stanford.edu
\\[0.0pc]Dr. Paul Mitiguy, Motion Genesis LLC and Stanford University Faculty, 650.346.9595,  mitiguy@stanford.edu
\\[0.0pc]Dr. Kaijen Hsiao, Bosch Research and Technology Center, 617.304.1759, kaijenhsiao@gmail.com
%\\[0.0pc]Oussama Khatib, Prof. Computer Science, 650.723.9753, khatib@cs.stanford.edu
}
%
\end{resume}
\end{document}







